
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Computer Vision and Biometrics Lab}
\descript{| Founding Member}
\location{Jan 2016 – Present | IIIT Guwahati, India}
I am a founding member of the Computer Vision and Bio-metrics Lab at IIIT Guwahati. where my research focuses in reducing friction between man and machine by exploiting techniques of cognitive science, affective computing , machine learning and computer vision.
\sectionsep

\runsubsection{UE HCI Lab, IIT Guwahati}
\descript{| Project Fellow}
\location{May 2016 – Jul 2016 | Guwahati, India}
\begin{tightemize}
\item Phabricator is used daily by Facebook, Dropbox, Quora, Asana and more.\item I created the Meme generator, the entire Lipsum application, ported Tokens to different apps, fixed many bugs and more in PHP and Shell.\item Led a team from MIT, Cornell, IC London and UHelsinki for the project.\end{tightemize}
\sectionsep

\runsubsection{Brahmaputra Innovative Solutions}
\descript{| Software Engineering Intern }
\location{May 2015 – Dec 2015 | Guwahati, India}
\begin{tightemize}
\item Worked on a document management system in primarily vanilla Javascript and Python to plan, design and develop the full stack implementation of a new framework to add and edit Automatic Speech Recognition captions.\item Created a backbone.js-like framework for the Captions editor.\item All code was reviewed, perfected, and pushed to production.\end{tightemize}
\sectionsep