\section{Scholarship}

\runsubsection{Chief Minister’s Scholarship to Meritorious Students of Assam}
\descript{}
\location{2014 - 2015}
\begin{tightemize}
	\item Only student of 3 institutes in the state is eligible for this one time scholarship.
\end{tightemize}
\sectionsep

\section{Projects}

\runsubsection{Dynamic Hand Gesture Recognition}
\descript{| Nov 2016 – Current}
\location{Mentor: Dr. Yezhou Yang (Arizona State University), Kuntal Dey (IBM Research Labs)}
Dynamic detection and classification of hand gestures in real-world systems is a challenging task. While approaches have
achieved state-of-the art accuracy using depth and stereo-IR sensors, we are exploring the use of simple RGB cameras for the task
of sign language recognition to provide a new modality of interaction for disabled people.

\sectionsep

\runsubsection{Ocular Biometrics and Iris Recognition in Visible Spectrum}
\descript{| Ma 2016 – Current}
\location{Mentor: Dr. Ferdous Ahmed Barbhuiya}
We are developing a system for verification and identification of individuals using iris and periocular features captured in the visible spectrum. We have investigated the use of traditional descriptors, novel ConvNet architectures with transfer learning and multi-modal feature extraction to achieve state-of-the art accuracy on standard bench-marking databases (VISOB and MICHE).
\sectionsep

\runsubsection{FaceTensor : Face Expression Analysis }
\descript{| Jan 2016 - Dec 2016}
\location{Mentor: Dr. Sandip Karmakar}
We have developed a state-of-the art system for facial expression recognition using a hybrid model from geometric
and appearance based features from near-frontal images and also performed an in-depth analysis as to which
emotions can be easily expressed as well as recognized by humans at a peak-intensity level from facial images.
\sectionsep

\runsubsection{TweeSpamAssassin: Spam Detection Engine in OSNs  }
\descript{| Jan 2015 – May 2015}
\location{Mentor: Dr. Ferdous Ahmed Barbhuiya}
\begin{tightemize}
	\item We investigated present models to detect spam on twitter.
	\item Inspired by email spam filter we developed a probabilistic based model to detect spam on twitter.
	\item The spam engine was deployed as bowsers plugin to filter out spam on twitter.
\end{tightemize}
\sectionsep

\runsubsection{Cryptographic Key Generation from PUF Data}
\descript{| Moonson 2014}
\location{Mentor: Dr. Ferdous Ahmed Barbhuiya}
\begin{tightemize}
	\item As a part of the project we build a cryptographic key generator from Physically Unclonable Functions Data using Efficient Fuzzy Extractors
\end{tightemize}
\sectionsep

\runsubsection{SLANG:  Native language writer}
\descript{| Spring 2014}
\skiplocation
\begin{tightemize}
	\item SLANG enables user write in their native language in English. Similar to what Google keyword (like “hinglish”) is doing.
	\item This was very simple implementation with no use of machine learning.
\end{tightemize}
\sectionsep

%\runsubsection{Academic Course Projects}

%\begin{skill-env}
%	\item \underline{Cloud Computing} - Developed an app on Amazon Web Service (using django, EC2, S3, SQS and EMR) that allows users to submit MapReduce jobs for Data Analysis. %The application is deployed on the Amazon Web Services, using Django to provide the MVC framework, EC2 instance for deployment, S3 for scalable storage, SQS for queuing jobs and EMR to perform the Map Reduce Job (this uses Hadoop framework for analytics).
%	\item \underline{Parallel Programming} - Using Parallel Python, I halved the verification time between two images by computing each modality of multi-modal biometrics in parallel (namely face, periocular and iris). 
%	\item \underline{Software Engineering} - Developed an online book-store with requirements engineering, use case diagrams, class diagrams, sequence diagrams and implementation with black box and white box testing.
%	\item \underline{Operating Systems} - Implemented a demand paged virtual memory, scheduler and shell program.
%	\item \underline{Computer Networks} - Development of a Multi-threaded Webserver in Linux over TCP and UDP.
%\end{skill-env}
\sectionsep